Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} Stagnating State Funding for Higher Education and its Effect on Faculty

### 2024-05-10 text/sections/09-figures-tables.tex
Fixed a spelling mistake.

\begin{table}[H]
    \singlespacing
    \centering
    \caption{First Stage Estimates, Predicting State Funding by Shift-Share shift-share in IPEDS Data.}
    \textbf{Panel A: units in \$ per student}

@@

\begin{table}[H]
    \singlespacing
    \centering
    \caption{Effects of State Funding on Faculty Counts, IPEDS 1990--2021, OLS and 2SLS Estimates.}

@@

\begin{table}[H]
    \singlespacing
    \centering
    \caption{Effects of Changes in State Funding on Faculty Salaries and Exit Rate, in Illinois 2010--2021, 2SLS Estimates.}
    \label{tab:faculty-shock-illinois-rolling}
    \makebox[\textwidth][c]{\input{tables/facultysalaries-shock-illinois-rolling.tex}}

>>>>

\begin{table}[H]
    \singlespacing
    \centering
    \caption{First Stage Estimates, Predicting State Funding by Funding Shift-Share, in IPEDS Data.}
    \textbf{Panel A: units in \$ per student}

@@

\begin{table}[H]
    \singlespacing
    \centering
    \caption{Effects of State Funding on Faculty Counts, in IPEDS Data 1990--2021, OLS and 2SLS Estimates.}

@@

\begin{table}[H]
    \singlespacing
    \centering
    \caption{Effects of State Funding on Faculty Salaries and Exit Rate, in IBHED Panel Data 2010--2021, 2SLS Estimates.}
    \label{tab:faculty-shock-illinois-rolling}
    \makebox[\textwidth][c]{\input{tables/facultysalaries-shock-illinois-rolling.tex}}
